---
title: "Day 3 Practice"
output: html_document
---

1. Make a "copy" of the `iris` data set in your workspace. Use `summary()` on it, identify a factor column.

```{r}
copy <- iris
summary(copy)
# Species is a factor
```

2. Create different versions of the factor column, in the new data set:
   a. a numeric vector with `as.numeric()`
   b. a character vector
   
```{r}
copy$species.num <- as.numeric(copy$Species)
copy$species.char <- as.character(copy$Species)
```

3. Use `xtabs()` to see how the values in these new columns line up with the original factor column.

```{r}
xtabs(~ Species + species.num + species.char, copy)
```

4. Check the order of levels of Species with `levels()`. Create a new column from this factor, changing the order of the levels, using:
  a. `relevel()`
  b. `reorder()`
  c. `factor()`

```{r}
levels(copy$Species)

# a.
copy$factorA <- relevel(copy$Species, "versicolor")
levels(copy$factorA)

# b.
copy$speciesOrder[copy$Species == "setosa"] <- 3
copy$speciesOrder[copy$Species == "versicolor"] <- 2
copy$speciesOrder[copy$Species == "virginica"] <- 1
copy$factorB <- reorder(copy$Species, copy$speciesOrder)
levels(copy$factorB)

# c. 
copy$factorC <- copy$Species
copy$factorC <- factor(copy$factorC, levels = c("versicolor", "setosa", "virginica"))
levels(copy$factorC)
```

5. Working with missing values
   - read in the data from "CognitionPaperModifiedData.csv"
   - locate NAs
   - display the rows of the data frame where the WithinMinPairs variable has missing values
   - create a new column that's a copy of the WithinMinPairs column
   - replace all missing values in this column with zeros
   - use `xtabs()` to check this change in coding *ignore; doesn't actually help; figure out another way to check*

```{r}
scottdata <- read.csv("../scottdata/CognitionPaperModifiedData.csv")
is.na(scottdata)
missing <- which(is.na(scottdata$WithinMinPairs))
missing
scottdata$WithinMinPairs.copy <- scottdata$WithinMinPairs
scottdata$WithinMinPairs.copy <- replace(scottdata$WithinMinPairs.copy, missing, 0)

#check coding change
scottdata$WithinMinPairs.copy[missing]
```

