---
title: "Day 7 Homework"
output: html_document
---

Find three relationships in your data.  For each relationship, do the following:

####1. Verbally articulate the relationship you want to examine.

**a.** relationship between Reading the Mind in the Eyes ("mind.eyes") and Theory of Mind Inventory ("ToM")

**b.** relationship between age and mind.eyes, with gender and full IQ (FIQ) also represented

**c.** relationship between age and Strange Stories Total Score ("strange.stories.total"), with gender also represented

####2. Verbally identify what variables you want to map to each graphical dimension.

**a.** ToM on the x-axis, mind.eyes on the y-axis

**b.** age on the x-axis, mind.eyes on the y-axis, each gender corresponds to a different color, and FIQ represented by point size

**c.** age on the x-axis, strange.stories.total on the y-axis, each gender corresponds to a different color

####3. Reshape your data as needed.

reshaping not needed; data saved as "mydata.RData" and uploaded to my GitHub repository
```{r}
load("mydata.RData")
```


####4. Use ggplot2 to create your graphs.

```{r}
library(ggplot2)

# a. ToM X mind.eyes 
scatterplot.a <- ggplot(mydata, aes(ToM, mind.eyes)) + geom_point()
scatterplot.a

# b. age X mind.eyes
scatterplot.b <- ggplot(mydata, aes(age, mind.eyes)) + geom_point(aes(color = gender, size = FIQ))
scatterplot.b

# c. age X strange.stories.total
scatterplot.c <- ggplot(mydata, aes(age, strange.stories.total)) + geom_point(aes(color = gender), size = 3)
scatterplot.c
```

####5. Fiddle with colors, axis labels, themes, etc. until the plot looks "publication ready" to you.  Try to change at least one thing per plot.

```{r}
library(scales)

# a. ToM X mind.eyes 
scatterplot.a + xlab("Theory of Mind Inventory") + scale_y_continuous(name = "Reading the Mind in the Eyes", labels = percent) + theme_minimal() 

# b. age X mind.eyes
scatterplot.b + scale_x_continuous(name = "Age (years)", breaks = seq(6, 13.5, .5)) + scale_y_continuous(name = "Reading the Mind in the Eyes", labels = percent) + theme_minimal() + scale_color_manual(values = c("springgreen4", "orange"), name = "Gender") + geom_smooth(color = "black", linetype = 3)

# c. age X strange.stories.total

scatterplot.c + scale_x_continuous(name = "Age (years)", breaks = seq(6, 13.5, .5)) + scale_y_continuous(name = "Strange Stories") + theme_minimal() + scale_color_manual(values = c("springgreen4", "orange"), name = "Gender") + geom_smooth(method = "lm", color = "black", linetype = 3) 

```


####6. Save all plots to a format that you could use in a paper.  HINT: PNG works well for pasting into Word documents.
```{r}
png("plot-a.png")
scatterplot.a + xlab("Theory of Mind Inventory") + scale_y_continuous(name = "Reading the Mind in the Eyes", labels = percent) + theme_minimal() 
dev.off()

png("plot-b.png")
scatterplot.b + scale_x_continuous(name = "Age (years)", breaks = seq(6, 13.5, .5)) + scale_y_continuous(name = "Reading the Mind in the Eyes", labels = percent) + theme_minimal() + scale_color_manual(values = c("springgreen4", "orange"), name = "Gender") + geom_smooth(color = "black", linetype = 3)
dev.off()

png("plot-c.png")
scatterplot.c + scale_x_continuous(name = "Age (years)", breaks = seq(6, 13.5, .5)) + scale_y_continuous(name = "Strange Stories") + theme_minimal() + scale_color_manual(values = c("springgreen4", "orange"), name = "Gender") + geom_smooth(method = "lm", color = "black", linetype = 3) 
dev.off()
```

